Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-07-17 main.tex
clean up

>>>>

\begin{lemma}    
    Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
    For $0 \leq m < M$, write 
    $$
        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m},
        \qquad 
        I_{m} := X_{m} \cap T_{m+1}.
    $$ 
    Then $I$ is the union of $k$ different facets of $T$, 
    and their intersection is a simplex $S \in \calT$ of dimension $n-k$.
    Moreover, 
    $$
        \patch_{X_{m+1}}(S) = \patch_{\calT}(S).
    $$
\end{lemma}
\begin{proof}
    We know $I_{m}$ is a submanifold of the boundary of $T$, and so it must be a collection of $k$ facets
    that constitute the local patch around some simplex $S$ of dimension $n-k$.
\end{proof}
